\rule{\textwidth}{4pt}\\[1em] \textbf{From Distribution Forecasts to Vanilla Portfolios: \\[0.2cm] Regularized Payoff Approximation in Discrete Space}\\[1em] \rule{\textwidth}{2pt}

### 2025-02-19 latex/article.tex
removed risk parameter in trading
comparison

\begin{figure}[htbp]
\centering
\input{regularization_comparison.tex}
\caption{Comparison of L1 and L2 regularization}
\label{fig:regularization}
\end{figure}

Figure~\ref{fig:regularization} demonstrates the effectiveness of both regularization 
approaches in approximating a complex payoff profile. The target function combines 
different types of functions, presenting a challenging test case. Both 
methods achieve good approximation quality, with L2 regularization providing slightly 
smoother results and L1 regularization favoring a sparser representation with fewer 
non-zero option weights.

\begin{figure}[htbp]
\centering
\input{weighted_loss.tex}
\caption{Weighted Error Method Performance}
\label{fig:weighted}
\end{figure}

Figure~\ref{fig:weighted} illustrates the performance of the weighted error method, 
which places greater emphasis on accurately approximating regions with larger payoff 
values. This approach is particularly useful when the economic significance of errors 
varies with the magnitude of the target payoff, providing a more practical solution 
for trading applications.

\section{Results}
\subsection{Distribution-Based Trading}
The approximation method enables novel trading strategies that exploit distributional 
forecasts rather than direct price predictions. Traders can hedge against forecasted 
distribution features, express views on higher moments of price distribution, and 
implement volatility surface arbitrage strategies through carefully constructed 
option portfolios.

The key advantage emerges when combining the approximation with distribution 
forecasts $\mathbb{P}(S_T)$:

\begin{equation}
\mathbb{E}[V(S_T)] = 
    \int_{0}^{\infty} 
        V(S) \mathbb{P}(S_T = S) dS
\end{equation}

Optimal portfolio weights $\boldsymbol{\theta}^*$ maximize the expected payoff under 
forecasted distribution:

\begin{equation}
\boldsymbol{\theta}^* = 
    \argmax_{\boldsymbol{\theta}} 
        \mathbb{E}\left[\hat{V}(S_T;\boldsymbol{\theta})\right] - 
        \lambda \text{Var}\left(\hat{V}(S_T;\boldsymbol{\theta})\right)
\end{equation}

where $\lambda$ represents risk aversion parameter.

@@

The results demonstrate that:
\begin{itemize}
    \item L2 regularization provides consistent performance across different $\gamma$ values,
    showing good stability in the approximation.
    \item L1 regularization achieves comparable accuracy while promoting sparser solutions,
    which can be advantageous for portfolio implementation.
    \item The weighted error method shows improved accuracy in regions with larger payoff
    values, as reflected in its MAE scores, particularly for moderate regularization values.
\end{itemize}

>>>>

\begin{figure}[htbp]
\centering
\input{regularization_comparison.tex}
\caption{Comparison of L1 and L2 regularization methods in approximating a complex payoff profile. 
While both methods achieve reasonable approximation quality, L2 regularization provides smoother results 
and L1 regularization favors a sparser representation with fewer non-zero option weights.}
\label{fig:regularization}
\end{figure}

\begin{figure}[htbp]
\centering
\input{weighted_loss.tex}
\caption{Performance of the weighted error method, demonstrating superior accuracy in regions 
with larger payoff values. This approach provides more economically meaningful results by 
emphasizing the approximation quality where it matters most for trading applications.}
\label{fig:weighted}
\end{figure}

@@

The results demonstrate that:
\begin{itemize}
    \item While L2 regularization provides an analytical solution and shows consistent performance 
    (MAE ~1.45), it may not be the optimal choice for practical applications.
    \item L1 regularization achieves comparable accuracy for low $\gamma$ values while promoting 
    sparser solutions, but its performance deteriorates significantly as regularization increases.
    \item The weighted error method consistently outperforms both L1 and L2 approaches, maintaining 
    superior accuracy (MAE ~1.04) across all tested regularization values. This makes it the most 
    suitable choice for real-world trading applications, where accuracy in high-payoff regions is 
    crucial for portfolio performance.
\end{itemize}

Despite the mathematical elegance and analytical tractability of the L2 approach, the empirical 
results strongly suggest that the weighted error method is more appropriate for practical 
implementation. Its ability to focus on economically significant regions and maintain consistent 
performance across different regularization parameters makes it the preferred choice for 
real-world trading applications.
